---
title: "Class_Final_Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Class_Final_Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(FALL224753bate0046)
```

# Functions

I have chosen 4 functions, and a data set from my package to upload for this assignment


## myhyper

Creates a simulation of a hypergeometric probability using the number of iterations, the total number of elements

The number of success in the N elements and the number of elements drawn

# Example:

```{r}
hyper=FALL224753bate0046::myhyper(100,20,10,8)
hyper
```

## myci

Creates the confidence interval of the mean given the samples and the confidence on the interval 

## Example:

```{r}
y=c(3,4,5,6,7,10)
cint=FALL224753bate0046::myci(y)
cint
```

## myboot2

Creates a confidence interval for the population mean for a given set of data by iterating subsets of a sample and calculating these samples means

## Example:
```{r}
set.seed(50)
sam=rnorm(10,mean=15,sd=12)
mb=FALL224753bate0046::myboot2(iter=10000,x=sam,fun="mean",alpha=0.05,xlab="mean",col=rainbow(12))
mb
```


## myncurve

Creates a graph of a normal curve with mean mu and standard deviation sigma

On this plot, it will also plot the lower tail area under the curve beginning at a, and print this value out to the console. 

## Example:
```{r}
FALL224753bate0046::myncurve(mu = 8, sigma = 3, a = 10)

```
## fire
The fire date used in previous labs, now able to load in using package

## Example:
```{r}
f=FALL224753bate0046::fire
f
mean(f$DISTANCE)
mean(f$DAMAGE)
```



