---
title: "Lab 4"
author: "Averi Bates"
date: '2022-09-16'
output: 
  html_document: 
        toc: yes
        toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Tasks


## Task 1

```{r}
getwd()
```

## Task 2

```{r}
spruce = read.csv("SPRUCE.csv")
tail(spruce)
```
## Task 3


```{r}
# Smooth Scatter Plot
library(s20x)
trendscatter(Height~BHDiameter,f=0.5,data=spruce)

```


```{r}
# Linear Model 
spruce.lm=with(spruce,lm(Height~BHDiameter)) 
summary(spruce.lm)
```



```{r}
# Residuals 
height.res=residuals(spruce.lm)
summary(height.res)

```


 
```{r}
# Fitted Values
fitted.res=fitted(spruce.lm)
summary(fitted.res)
```
 
```{r}
plot(x= fitted.res, y=height.res)
```
 

```{r}
trendscatter( y= height.res, x= fitted.res)
```


 The shape in this plot comparing residuals vs. fitted values is a curvy downward slope of the data. The data climbs upward before going down. The other trendscatter plot was just a curved line trend in the data. 
 
 The pvalue in this case is 2.089e-09. 

```{r}
windows()
normcheck(spruce.lm,shapiro.wilk = TRUE)

```

The pvalue for this plot is 0.29.

```{r}
# Residual Plot 
plot(spruce.lm, which = 1)
```




## Task 4



```{r}
# Quadratic Model
library(s20x) 
trendscatter( fitted.res,height.res)
windows()
plot(Height~BHDiameter,bg="Blue",pch=21,cex=1.2,
ylim=c(0,max(Height)),xlim=c(0,max(BHDiameter)), 
main="Spruce Height Prediction",data=spruce)
quad.lm=lm(Height~BHDiameter + I(BHDiameter^2),data=spruce)
summary(quad.lm)

coef(quad.lm)
names(quad.lm)
quad.lm$coef[2]

myplot=function(x){
 0.86089580 +1.46959217*x  -0.02745726*x^2
}
curve(myplot, lwd=2, col="purple",add=TRUE) 

```

```{r}
quadfit = fitted(quad.lm)
summary(quad.lm)
```

```{r}
# Residuals vs. Quadratic Line
plot(quad.lm, which=1)
```



```{r}
# Normality Check
windows()
normcheck(quad.lm,shapiro.wilk = TRUE)
```





## Task 5


```{r}
summary(quad.lm)
```

B hat values 

Bhat sub 0 = 0.86089580

Bhat sub 1 = 1.4959217

Bhat sub 2 = -0.027457

 

```{r}
# Interval Estimates
ciReg(quad.lm)
```
Equation of Fitted Line

y = 0.0860896 + 1.469x - 0.0274x^2

```{r}
predict(quad.lm, data.frame(BHDiameter=c(15,18,20)))
```

```{r}
predict(quad.lm, data.frame(BHDiameter= c(3,6,8)))
```


The value for multiple R^2 in the quadratic equation model is 0.77 and the multiple R^2 for the spruce scatter plot is 0.6569. 

The adjusted R^2 for the quadratic line is 0.76 and the adjusted for the spruce scatter plot is 0.6468. 

The value for multiple R^2 for the quadratic line is a much better representation of the data because a higher percentage is explained by the plot. 




```{r}
# Variability in Height

##Anova
anova(spruce.lm)
anova(quad.lm)
anova(spruce.lm,quad.lm)
```



```{r}
# TSS 
TSS = with(spruce, sum((Height-mean(Height))^2))
TSS
```


```{r}
# RSS 
height.fit=fitted(spruce.lm)
RSS=with(spruce, sum((Height-height.fit)^2))
RSS
```

```{r}
#MSS
MSS = with(spruce, sum((height.fit-mean(Height))^2))
MSS
```

```{r}
#MSS/TSS
MSS/TSS
```


## Task 6

```{r}
# Cooks Plot 
cooks20x(quad.lm)
```

Cooks Distance is used to determine the importance of a data point when conducting a regression analysis. Points with a higher distance may distort the accuracy of the plot, and are less important.   

Cooks Distance means some data points matter more then others. 
```{r}
quad2=lm(Height~BHDiameter + I(BHDiameter^2) , data=spruce[-24,])
summary(quad2)
summary(quad.lm)
```
The new object above removed the outlier number 24. After doing this the mulitple R^2 increased to 0.81 which is a more accurate representtion of the data.

## Task 7

   \begin{eqnarray}

\beta_0 +\beta_1 x_k &=& \beta_0\ - \beta_2x_k + (\beta_1+\beta_2)x_k\\ 
y&=& \beta_0 -\beta_2x_k + (\beta_1 +\beta_2)x\\
y&=& \beta_0 + \beta_1 x +\beta_1 + \beta_2(x-x_k)I(x>x_k)
\end{eqnarray} 


```{r}
sp2.df=within(spruce, X<-(BHDiameter-18)*(BHDiameter>18)) 
sp2.df

lmp=lm(Height~BHDiameter + X,data=sp2.df)
tmp=summary(lmp)
names(tmp)
myf = function(x,coef){
  coef[1]+coef[2]*(x) + coef[3]*(x-18)*(x-18>0)
}
plot(spruce,main="Piecewise regression")
myf(0, coef=tmp$coefficients[,"Estimate"])
curve(myf(x,coef=tmp$coefficients[,"Estimate"] ),add=TRUE, lwd=2,col="Blue")
abline(v=18)
text(18,16,paste("R sq.=",round(tmp$r.squared,4) ))

 
```



## Task 8

```{r}
library(FALL224753bate0046)
carb = read.csv("CARBON.csv")
with(carb, scatterhist(PilotPlant, LabFurnace, xlab="PilotPlant"))

```

The function creates to basic graphs for categorical data, a pie chart and a bar plot. 






